Title

### 2014-07-24 paper.tex
added more discussion

\noindent \textbf{RQ1:} Can we identify useful and useless discussions in code review?\\
\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?

@@

\section{Empirical Study}

@@

In total, there are 6,605 changes and 72,484 comments. 25,076 comments are by the system or one of the bots.

@@

Many common patterns are found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
The occurrences of these patterns are removed from our data set.
This leaves 36,738 comments empty, which probably means that the whole comment is automatically generated.
Only 17,275 comments and commit messages are left.

@@

After preprocessing, 393,238 tokens are generated in total. They are composed of 20,025 different words.
This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.

@@

% noisy data, and binary classification

% tuning the F score for precision and recall

% reasons for classification as useful or not useful

>>>>

\noindent \textbf{RQ1:} Can we identify useful and useless discussions in code review?\\
\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
\noindent \textbf{RQ3:} Is this a cost-efficient way to identify useful and useless comments?

@@

\section{Case Study}

@@

\begin{figure}[h]
\centering
\includegraphics[width=3.2in]{filter}
\caption{The filtering process.}
\label{fig:filter}
\end{figure}

\subsubsection{Data extraction}

6,605 changes and 72,484 comments have been extracted from the raw dataset.
35\% of the comments are by the system or one of the bots, and are thus discarded.

@@

By looking for most frequent lines, common patterns were found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.

Removing occurrences of these patterns leaves 77\% of the remaining comments empty.
This probably means these comments solely contain automatically-generated text, and are thus discarded.
This leaves us with 10,670 comments and 6,605 commit messages; a total of 17,275 documents.

@@

After the tokenization step, 393,238 tokens are generated in total. They are composed of 20,025 different words.
This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.

@@

% noisy data, and binary classification
Our training data is very noisy because there are disagreements between our judgment of ``usefulness.''
These samples cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.

By removing the samples with scores of 1 and 2, leaving with 209 samples without disagreements, and performing 10-fold cross-validation, we received a much better average F$_1$ score of 0.896.

% tuning the F score for precision and recall
Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
For instance, if we wanted to measure the amount of useful comments within a large dataset, we can give more weight to precision, sacrificing some good comments.
If we wanted to modify a code review software such that it displays useful comments more prominently, we can give more weight to recall.

% reasons for classification as useful or not useful
During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:

\begin{itemize}
	\item they contain new information;
	\item they contain constructive suggestions;
	\item they discuss directly about the change; and
	\item they discuss technical matters.
\end{itemize}

Examples of reasons for negative comments include:

\begin{itemize}
	\item chatting (i.e. no new information, just communication);
	\item not discussing directly about the change;
	\item discussing about the process workflow; and
	\item discussing about Git or Gerrit itself.
\end{itemize}
